\huge Tor's Usability for Censorship Circumvention

### 2016-04-25 pets2017-paper/pets2017-paper.tex
Explain the × notation in all-participant-edges figure.
david's suggestions

  \begin{abstract}
{Tor has grown beyond its original purpose as an anonymity tool and has 
become a widely-used censorship circumvention tool.
This is the first study to examine Tor's usability as a censorship circumvention tool.
We evaluate, redesign, and test the Tor configuration interface by
placing users in simulated censorship environments, instruct them to use Tor
to circumvent censorship, and measuring their interactions with the interface.
A 16-participant qualitative user study identifies common user struggles while circumventing censorship.
We use the results as feedback to redesign the configuration interface.
A 124-participant quantitative user study tests the impact of our changes
to find that our changes results in a significant reduction 
in the spent configuring a connection, while maintaining the same rate of success. We
conclude with recommendations for changes to the current configuration interface and discuss
alternative configuration processes with different balances of risk, automation, and user input.}
\end{abstract}
  \keywords{User Studies, Tor, Security, Censorship, Anonymity}
%  \classification[PACS]{}
 % \communicated{...}
 % \dedication{...}

@@

Tor is an anonymity network that routes traffic through a series of relays
that makes it difficult to observe the source and destination~\cite{dingledine2004tor}. Tor's anonymizing functionality coincidentally also circumvented censorship. Eventually, censorship circumvention became a common enough use case for Tor that many countries attempt to block Tor for that reason~\cite{winter2012great}. Today, Tor explicitly provides support for censorship circumvention through a network of unlisted relays as entry points into the Tor network, various methods of obfuscation to make connections to the Tor network indistinguishable, and advanced techniques to resist blocking.

This is the first user study investigating the usability of Tor as a censorship circumvention tool. Our experiments are both a case study of observing users circumvent censorship, and a step toward helping current Tor users by making censorship circumvention easier. All Tor users will benefit from improving the configuration interface, and therefore increasing the adoption of Tor as a censorship circumvention tool. Users who successfully use Tor to circumvent censorship will be provided with extra security features that other censorship circumvention tools do not provide, while users who use Tor as an anonymity system benefit from an increased the number of overall users on the Tor network~\cite{dingledine2006anonymity}.

We evaluate, redesign, and test the Tor configuration interface by
measuring participants' interactions with the interface in various censorship environments.
The first user study is a small-scale, one-on-one experiment that collected 
behavioral patterns and failure cases with the interface through user observations
and interviews (Section~\ref{sec:qualitative}). This feedback was used to make changes to the interface (Section~\ref{redesign}). The second user study is a large-scale, data-centric user study
that collected data on user interactions with the interface to quantify the impact of the design changes (Section~\ref{sec:quantitative}).

We find that users do not know if they require additional configuration to circumvent censorship, make incorrect assumptions based on interface layout, and do not know what to do in the event of a failure. We redesign the interface to build users' mental models, provide instructive text, and assist on error. These changes decreased the time participants spent configuring their connections, with no decrease in success rates. We conclude with recommendations of changes that we believe will help the most users circumvent censorship and connect to Tor.

@@

There have been been no published usability evaluations of
Tor Browser since the 3.5 series, which introduced radical UI changes~\cite{torbrowser-35}.
The most recent usability effort is an unpublished pilot study by Lee and Fifield~\cite{uxsprint} 
that tested the downloading, installation, and browsing tasks in Tor Browser.  This study uncovered a number of issues~\cite{uxsprint2015-tickets},
some of which influenced changes in Tor Browser version~4.5 and later.

@@

\section{Background}
This section talks about how the configuration interface relates to Tor, what network components are involved in censorship circumvention, and which configuration settings are required to bypass levels of Tor-adverse censorship environments.

\subsection{Tor, Tor Browser, and Tor Launcher}
The recommended way to use Tor is through Tor Browser~\cite{torbrowser},
a modified Firefox browser that includes a built-in Tor client.
Tor Browser has a software component called Tor Launcher that
starts, stops, and otherwise controls the underlying Tor processes.
Tor Launcher's graphical user interface gives access to a variety of 
sophisticated circumvention mechanisms, asking the user
to configure a proxy and bridge (if necessary) before connecting to Tor
for the first time. This is the target of our study.

In principle, the process of configuring a proxy and bridge can be automated, but
the interface eschews automatic configuration through network probing
in favor of guided manual configuration to give users agency in configuring their connection.
A knowledgeable user can minimize their network trace and hide that they are connecting to Tor.
However, this burdens the user to grapple with technical concepts such as 
bridges, pluggable transports, and proxies and to configure their connection correctly.

@@

Bridges are unlisted Tor relays that make it possible for a user to connect
to the Tor network even if a censor blocks all publicly listed Tor relays.
Pluggable transports are special protocols that run on bridges and obfuscate
Tor's network protocol to make it difficult to detect. 
Configuring a bridge requires providing one or more
``bridge lines,'' a specification of a bridge that
includes its IP address, transport type, and other metadata.
For ease of use, the interface has hard-coded options for 
the user to choose a group of bridges that use a particular
pluggable transport. For example, choosing  the hard-coded ``obfs3'' option
configures a handful of bridges that use obfs3 pluggable transport.
Some censors block the IP addresses of the hard-coded bridges by looking
at the source code for those addresses (except ``flashproxy'' and ``meek,'' which work differently).
If the built-in bridges do not work, a user can obtain bridge lines
through out-of-band channels, for instance by email~\cite{bridgedb}.

@@

\begin{figure}
\small
\begin{itemize}
\renewcommand{\labelitemi}{$\circ$}
\item Connect with provided bridges\\
Transport type:
\begin{itemize}
\item flashproxy
\item fte
\item fte-ipv6
\item meek-amazon
\item meek-azure
\item meek-google
\item obfs3 (recommended)
\item obfs4
\item scramblesuit
\end{itemize}
\item Enter custom bridges\qquad\fbox{Help}\\
\end{itemize}
\caption{
Bridge selection options in Tor Launcher, as it appeared in Tor Browser~5.0.3.
The obscure strings under ``Transport type'' denote various
built-in circumvention technologies (``pluggable transports'').
Under ``Enter custom bridges,'' there is a space to paste in
a bridge line, obtained out of band.
The ``Help'' button displays instructions on obtaining
bridge lines.
}
\label{fig:bridge-options}
\end{figure}

In addition to Tor-specific components, a proxy may be necessary to connect 
outside the local network in certain managed networks, such as corporate or university networks.
Configuring a proxy requires providing the proxy protocol, IP address, port and additional optional
fields. There is no assistance or automation with this process. The user must locate the 
proxy information and correctly format this information into the configuration interface.

@@

Uncensored users and users in censorship environments that do not explicitly 
block Tor do not require a bridge nor a proxy and can bypass the configuration process.
Users in censorship environments that explicitly block Tor but has not blocked the 
hard-coded bridges in the Tor Launcher source code are required to use a 
hard-coded bridge or custom bridge to connect to Tor. Users in a censorship environment that has explicitly 
blocked Tor relays and hard-coded bridges will be required to configure a meek bridge (which 
routes traffic through content delivery networks and therefore resists blocking via collateral damage) or 
configure a custom bridge to connect to Tor.

\section{Evaluation Criteria and Goals}
\label{sec:goals}
The series of user studies evaluated two versions of the Tor Launcher interface.
The first, which we have labeled ``OLD'' in figures and tables,
is the current version being distributed with Tor Browser.
The second, ``NEW,'' is the prototype we revised and redesigned
in order to provide better usability. Below are the empirical and 
heuristic evaluation criteria we use to assess the interfaces.

@@

\noindent {\bfseries Challenge 3: Users did not know how to choose which bridge and pluggable transport.}
On the bridge configuration screen, participants were intimidated by the names of the bridge transports. The most common behavior was to configure with the recommended bridge option (obfs3). If the recommended one did not work, participants did not know how to choose another.

@@

\noindent {\bfseries Challenge 4: Users do not know when they are wrong.} 
Unfortunately, many mistakes did not result in error messages, bu warnings that went unnoticed.
When participants did encounter an error message, they did not understand what errors meant (Fig.~\ref{fig:error}).\\

@@

We augmented the interfaces with instrumentation 
to log every meaningful interaction
(button presses, menu selections, screen changes).
We wrote scripts to automatically set up the simulated censorship environment, install necessary software, 
start the video recording, and save the logs and videos.
We recorded the participants' computer screens
throughout the experiment to capture non-interface activity such as 
web searching and inspection of system networking settings.

@@

\subsection{Procedure}
The one-hour, multi-participant procedure begins when all participants are sitting at their
respective computers in Xlab. Each computer is equipped with an instrumented old or new version
of Tor Browser, Chrome, Firefox, Internet Explorer,  Chrome, and VLC (for screen recording).
Each computer was assigned one of the six conditions in the beginning of the study. Participants
were assigned to the seats at random, effectively being assigned a configuration launcher and
simulated censorship environment combination at random.

@@

\subsection{Results} 
Out of our 124 recruited participants, 116 provided valid data. We have 58 participants who tested the new interface, and 58 who tested the old interface. 38 participants were in E1, 38 participants were in E2, and 40 participants were in E3. Since our experiment ended after 40 minutes, we chose to assign the maximum time of 40:08 minutes to participants who did not succeed. Table~\ref{table:participant-summary} summarizes the rate of success and time to success for our participants' based on their interface version and environment combination.

@@

Table~\ref{tab:attempts-bridge-proxy} shows the configuration settings of the first successful bootstrap in each environment and interface combination. Note that only four of the default bridges were used to connect successfully for the first time. Users avoid making decisions when a recommendation is given and tend to avoid/fail with more advanced options. Participants who were in environments in which the recommended bridge (obfs3) worked did not configure another bridge, not taking advantage of the various default bridges available to them. Participants who were in environment that required a meek or custom bridge only were able to succeed with a meek bridge.

@@

In our experiment, participants had 40 minutes to circumvent censorship. Fig.~\ref{fig:time_to_success_ecdf} shows the cumulative success rates over time. Participants were less and less likely to succeed as time went on. Users in the wild will likely not be motivated to configure their connection for 40 minutes. Table~\ref{table:less_time} shows that if users were only willing to put in a minute or so of their time, users in intermediate and heavily censored environments will be unable to connect. Even if users were willing to dedicate 10 minutes to configuring their connection, most users in heavily censored environments will be unable to connect. Ideally, users should be able to connect to Tor within a couple of minutes, regardless of their censorship environment. We propose ideas on how to achieve this in section~\ref{recommendations}.

\begin{figure}
\centering
\includegraphics{time_to_success_ecdf}
\caption{
Cumulative success rates over time, by censorship environment and interface.
We stopped participants after 40 minutes. Here, those who did not finish were assigned
an arbitrarily high number greater than 40 minutes for the purposes of plotting. 
}
\label{fig:time_to_success_ecdf}
\end{figure}

\begin{table}
\centering 
	% Generated by info.R:
	\begin{tabular}{l r r r r}
	& \multicolumn{1}{c}{1.5~m} & \multicolumn{1}{c}{10~m} & \multicolumn{1}{c}{20~m} & \multicolumn{1}{c}{40~m} \\
	\noalign{\hrule}
	E1-NEW & 100\% & 100\% & 100\% & 100\% \\
	E1-OLD & 58\% & 100\% & 100\% & 100\% \\
	E2-NEW & 11\% & 79\% & 89\% & 95\% \\
	E2-OLD & 16\% & 68\% & 79\% & 84\% \\
	E3-NEW & 0\% & 25\% & 45\% & 65\% \\
	E3-OLD & 0\% & 20\% & 25\% & 50\% \\
	\end{tabular}
\caption{This Table shows what the success rate would have been
at different cutoff times.
For example, every E1-NEW participant finished within 90 seconds,
but only 58\% of E1-OLD had finished by that time.
After 10 minutes, 79\% of E2-NEW and 68\% of E2-OLD had finished.
After 20 minutes, 45\% of E3-NEW and only 25\% of E3-OLD had finished.}
\label{table:less_time}
\end{table}

@@

\begin{figure*}
\centering
% This is a manually edited version of the automatically generated
% all-participant-edges graphic. It is edited to have better scale labels for
% the treatments.
\includegraphics{all-participant-edges-scales}
\caption{
Summary of participants' actions throughout the entire experiment.
Different colors indicate which screen was shown at each moment.
The narrow black lines show the times when the configuration interface
was not running; i.e., a participant was doing something else
such as searching the web in another browser.
The overall length of the lines show the total time to completion,
except for those we cut off after approximately 40 minutes.
}
\label{fig:all-participant-edges}
\end{figure*}

@@

Perhaps a more meaningful measurement of time is the amount of time participants actively spent configuring their connection. We define this as the amount of time that participants spent on the interface, except for time spent on the progress screen. This is a simplified notion active configuration time, since some participants searched for help on the web while they were waiting. However, this behavior was equally likely in the new and old interface conditions.

@@

\begin{description}
%connect vs configure
\item {\bfseries Users try the easy path first.} Users still do not seem to know how to differentiate between censored websites and censored Tor relays, and just try the easy option to connect directly to the Tor network first, leaking that they are connecting to Tor on the network.  81\% (94 of 116) of first attempts were to connect directly, 86\% (50 of 116) from the new interface and 76\% (44 of 116) from the old interface.

% impacts of making the proxy page ``automated'' 
\item {\bfseries Users wasted time configuring proxies.} Users believed that they needed proxies to connect. This confusion prevented users from configuring their bridges correctly. Participants with the new interface who were explicitly told that they did not need a proxy spent 31\% of their active time configuring proxies and participants in the old interface who did not receive feedback spent 63\%.

@@

\subsubsection{Reasons for Failure} 
Failure is common. 64\% (74 of 116) of first attempts to connect failed and 79\% (376 of 462) of total attempts to connect failed. 20\% (22 of 116) of participants failed entirely. Reasons for failure were determined by a combination of log processing (i.e., how much time was spent on a particular screen) and video observation (i.e., observing what they searched for online). \\

\begin{description}
\item {\bfseries Only connected directly. (8/23)} These participants tried a direct connection. When that failed, they tried the same configuration, over and over, without trying other configurations, no matter how many times they failed. It was common to restart the interface, check Internet settings, and wait between subsequent attempts. 
\item {\bfseries Did not know what to do next. (6/23)} After a failed direct connection and a failed default obfs3 bridge connection, these participants did not know what to do next. They often tried those configurations again or gave up. 
\item {\bfseries Thought that they needed a proxy (5/23)} After a couple failed attempts, these participants assumed that they needed a proxy. They spent the time trying to configure a proxy, usually without trying other bridges. 
\item {\bfseries Used the bridges auto-responder incorrectly (3/23)} Three participants in our heavy censorship environment figured that the recommended bridge and most hard-coded bridges were not working and found the auto-responder through the help button. However, they all failed to get a response. For details, see Appendix~\ref{failed-participants}.
\end{description}

We discarded data on participants who chose to download their own version of Tor Browser online. Some downloaded their own version without trying the provided one on their desktop, while others did so after feeling frustrated with the provided version. Appendix~\ref{tor-downloads} gives the unfortunate details of where Tor was downloaded when torproject.org was blocked.

@@

We did not test cases in which the user is required to configure a custom bridge or proxy. Our participants were from one geographic location in the United States and were able to speak English.

\section{Future Work} 
Throughout the qualitative user study, redesign of the interface, and the quantitative user study, we collaborated and communicated with Tor developers. Redesigning the configuration interface was a mutual interest. In fact, Tor version~4.5 incorporated textual and navigational changes based on our redesigned interface. We plan to work with Tor developers to integrate helpful changes. This process will entail debugging our code, merging changes with the current version of Tor, making high-fidelity graphics that align with style guides, and finalizing the advice to give to users in the interface.

@@

\begin{description}
\item{\bfseries Automate the configuration.} Complete automation and network probing sounds like a radical idea, but this would not harm users today (as far as we know). Most users would leak that they are using Tor when trying to circumvent an advanced censor, since most first attempts to connect fail. 
\item{\bfseries Ask about the risk.} Ask the users if they would be at risk if the process was automated, and automate the configuration process for all who are not at risk. The ones at risk will configure manually. The complication with this approach is that users may not be qualified to answer this question or may not trust Tor to answer honestly. 
\item{\bfseries Ask if users if they know what to do.} We ask users if they know how to configure a bridge and proxy, and automate the configuration process if they do not. However, there are ethical implications of making mistakes on behalf of the users if there is risk involved. 
\end{description}

@@

%\section {Acknowledgments}
%{\color {red} Rowilma del Castillo for setting up Xlab, Nima Fatemi, Isabela Bagueros, Georg Koppen, and the UX team for giving feedback, and Cecile Basnage for reviewing the UI of circumvention tools.} 
%{\color {red} Tor Browser devs for taking our recommendations to heart and implementing changes.}

\section{Conclusion} 
We conducted a series of experiments to improve the Tor Browser 5.0.3 configuration interface, which helps users circumvent censorship using Tor. The qualitative user study interviews 16 pre-screened participants about their experience trying to circumvent mild, intermediate, and heavy censorship with the current interface, giving insight into common challenges in configuring a connection, such as confusing the necessity of bridges and proxies, assuming that a correct configuration was wrong due to a progress bar bug, and not knowing what to do on failure. This feedback is used to guide the redesign of the configuration interface.

We test the impact of our changes on 124 participants in the quantitative user study to find that that the changes made cause a statistically significant reduction in the time participants spent configuring their connection, with no decrease in success rates. We observe and quantify common behavioral trends based on logs and video recordings of our participants, and offer recommendations that we believe will greatly increase the success rate and time to success for future users.

@@

Only tried to connect directly (8/23): 
\begin{itemize}
\item E2-NEW-X21-20160323-1400
\item E2-OLD-X04-20160330-1800
\item E2-OLD-X10-20160331-1600
\item E3-NEW-X05-20160324-1400
\item E3-NEW-X17-20160323-1400
\item E3-OLD-X06-20160328-1400
\item E3-OLD-X06-20160330-1600
\item E3-OLD-X12-20160330-1800
\end{itemize}

Did not know what to do next (6/23): 
\begin{itemize}
\item E3-NEW-X11-20160330-1600
\item E3-NEW-X11-20160331-1800
\item E3-NEW-X23-20160323-1400
\item E3-OLD-X06-20160331-1800
\item E3-OLD-X12-20160331-1600
\item E3-OLD-X30-20160328-1400
\end{itemize}

>>>>

  \begin{abstract}
{Tor has grown beyond its original purpose as an anonymity tool and has 
become a widely-used censorship circumvention tool.
This is the first study to examine Tor's usability as a censorship circumvention tool.
We evaluate, redesign, and test the Tor 5.0.3 configuration interface by
placing users in simulated censorship environments, instruct them to use Tor
to circumvent censorship, and measuring their interactions with the interface.
A 16-participant qualitative user study identifies common user struggles while circumventing censorship.
We use the results as feedback to redesign the configuration interface.
A 116-participant quantitative user study tests the impact of our changes
to find that our changes results in a significant reduction 
in the spent configuring a connection, while maintaining the same rate of success. We
conclude with recommendations for changes to the current configuration interface and discuss
alternative configuration processes with different balances of risk, automation, and user input.}
\end{abstract}
  \keywords{User Studies, Tor, Security, Censorship, Anonymity}
%  \classification[PACS]{}
 % \communicated{...}
 % \dedication{...}

@@

Tor~\cite{dingledine2004tor} is an anonymity network that routes traffic through a series of relays
that makes it difficult to observe the source and destination. Tor's anonymizing functionality coincidentally also circumvented censorship. Eventually, censorship circumvention became a common enough use case for Tor that many countries attempt to block Tor for that reason~\cite{winter2012great}. Today, Tor explicitly provides support for censorship circumvention through a network of unlisted relays as entry points into the Tor network, various methods of obfuscation to make connections to the Tor network indistinguishable, and advanced techniques to resist blocking.

This is the first user study investigating the usability of Tor as a censorship circumvention tool. Our experiments are both a great a case study of observing users circumvent censorship, and a step to help current Tor users by making censorship circumvention easier. All Tor users will benefit from improving the configuration interface, and therefore increasing the adoption of Tor as a censorship circumvention tool. Users who successfully use Tor to circumvent censorship will be provided with extra security features that other censorship circumvention tools do not provide, while users who use Tor as an anonymity system benefit from an increased the number of overall users on the Tor network~\cite{dingledine2006anonymity}.

We evaluate, redesign, and test the Tor 5.0.3 configuration interface by
measuring participants' interactions with the interface in various censorship environments.
The first user study is a small-scale, one-on-one experiment that collected 
behavioral patterns and failure cases with the interface through user observations
and interviews (Section~\ref{sec:qualitative}). This feedback was used to make changes to the interface (Section~\ref{redesign}). The second user study is a large-scale, data-centric user study
that collected data on user interactions with the interface to quantify the impact of the design changes (Section~\ref{sec:quantitative}).

We find that users don't know if they require additional configuration to circumvent censorship, make incorrect assumptions based on interface layout, and do not know what to do in the event of a failure. We redesign the interface to build users' mental models, provide instructive text, and assist on error. These changes decreased the time participants spent configuring their connections, with no decrease in success rates. We conclude with recommendations of changes that we believe will help the most users circumvent censorship and connect to Tor.

@@

There have been been no published usability evaluations of
Tor Browser since the 3.5 series, which introduced radical UI changes~\cite{torbrowser-35}.
The most recent usability effort is an unpublished pilot study by Lee and Fifield~\cite{uxsprint} 
that tested the downloading, installation, and browsing tasks in Tor Browser.  This study uncovered a number of issues~\cite{uxsprint2015-tickets},
some of which influenced changes in Tor Browser version~5.1 and later.

@@

\section{Background}
This section talks about how the configuration interface relates to Tor, what the network components are involved in censorship circumvention, and which configuration settings required to bypass levels of Tor-adverse censorship environments.

\subsection{Tor, Tor Browser, and Tor Launcher}
The recommended way to use Tor is through Tor Browser~\cite{torbrowser},
a modified Firefox browser that includes a built-in Tor client.
Tor Browser has a software component called Tor Launcher that
starts, stops, and otherwise controls the underlying Tor processes.
Tor Launcher's graphical user interface gives access to a variety of 
sophisticated circumvention mechanisms, asking the user
to configure two a proxy and bridge (if any) before connecting to Tor
for the first time. This is the target of our study.

In principle, the process of configuring a proxy and bridge can be automated, but
the interface eschews automatic configuration through network probing
in favor of guided manual configuration to give users agency in configuring their connection.
A knowledgeable user can minimize their network trace and hide that they are connecting to Tor.
However, this burdens on the user to grapple with technical concepts such as 
of bridges, pluggable transports, and proxies and to configure their connection correctly.

@@

Bridges are unlisted Tor relays that make it possible for a user to connect
to the Tor network even if a censor blocks all publicly listed Tor relays.
Pluggable transports are special protocols that run on bridges and obfuscate
Tor's network protocol to make it difficult to detect. 
Configuring a bridge requires providing one or more
``bridge lines,'' a specification of a bridge that
includes its IP address, transport type, and other metadata.
For ease of use, the interface has hard-coded options for 
the user to choose a group of bridges that use a particular
pluggable transport. For example, choosing  the hard-coded``obfs3'' option
configures a handful of bridges that use obfs3 pluggable transport.
Some censors block the IP addresses of the hard-coded bridges by looking
at the source code for those addresses (except ``flashproxy'' and ``meek,'' which work differently).
If the built-in bridges do not work, a user can obtain bridge lines
through out-of-band channels, for instance by email~\cite{bridgedb}.

@@

\begin{figure}
\small
\begin{itemize}
\renewcommand{\labelitemi}{$\circ$}
\item Connect with provided bridges\\
Transport type:
\begin{itemize}
\item flashproxy
\item fte
\item fte-ipv6
\item meek-amazon
\item meek-azure
\item meek-google
\item obfs3 (recommended)
\item obfs4
\item scramblesuit
\end{itemize}
\item Enter custom bridges\qquad\fbox{Help}\\
\end{itemize}
\caption{
Bridge selection options in Tor Launcher, as it appeared in Tor Browser~5.0.3.
The obscure strings under ``Connect with provided bridges'' denote various
built-in circumvention technologies (``pluggable transports'').
Under ``Enter custom bridges'', there is a space to paste in
a bridge line, obtained out of band.
The ``Help'' button displays instructions on obtaining
bridge lines.
}
\label{fig:bridge-options}
\end{figure}

In addition to tor-specific components, a proxy may be necessary to connect 
outside the local network in certain managed networks, such as corporate or university networks.
Configuring a proxy requires providing the proxy protocol, ip address, port and additional optional
fields. There is no assistance or automation with this process. The user must locate the 
proxy information and correctly format this information into the configuration interface.

@@

Uncensored users and users in censorship environments that do not explicitly 
block Tor do not require a bridge nor a proxy and can bypass the configuration process.
Users in censorship environments that explicitly block Tor but has not blocked the 
hard-coded bridges in the Tor Launcher source code are required to use a 
a hard-coded bridge or custom bridge to connect to Tor. Users in a censorship environment that has explicitly 
blocked Tor relays and hard-coded bridges will be required to configure a meek-bridge (which 
routes traffic through content delivery networks and therefore resists blocking via collateral damage) or 
configure a custom bridge to connect to Tor.

\section{Evaluation Criteria and Goals}
\label{sec:goals}
The series of user studies evaluated two versions of the Tor Launcher interface.
The first, which we have labeled ``OLD'' in figures and tables,
is the current version being distributed with Tor Browser.
The second, ``NEW'', is the prototype we revised and redesigned
in order to provide better usability. Below are the empirical and 
heuristic evaluation criteria we use to assess the interfaces.

@@

\noindent {\bfseries Challenge 3: Users did not know how to choose which bridge and pluggable transport.}
On the bridge configuration screen, participants were intimidated by the names of the bridge transports. The most common behavior was to configure with the recommended bridge option (obfs3). If the recommended one did not work, participants didn't know how to choose another.

@@

\noindent {\bfseries Challenge 4: Users do not know when they are wrong.} 
Unfortunately, many mistakes did not result in error messages, bu warnings that went unnoticed.
When participants did encounter an error message, they did not understand what errors meant (Figure~\ref{fig:error}).\\

@@

We augmented the interfaces with instrumentation 
to log every meaningful interaction
(button press, every menu selection, every screen change).
We wrote scripts to automatically set up the simulated censorship environment, install necessary software, 
start the video recording, and save the logs and videos.
We recorded the participants' computer screens
throughout the experiment to capture non-interface activity such as 
web searching and inspection of system networking settings.

@@

\subsection{Procedure}
The one-hour, multi-participant procedure begins when all participants are sitting at their
respective computers in Xlab. Each computer is equipped with an instrumented old or new version
of Tor Browser, Chrome, Firefox, Internet Explorer,  Chrome, and VLC (for screen recording).
Each computer was assigned one of the 6 conditions in the beginning of the study. Participants
were assigned to the seats at random, effectively being assigned a configuration launcher and
simulated censorship environment combination at random.

@@

\subsection{Results} 
Out of our 124 recruited participants, 116 provided valid data. We have 58 participants who tested the new interface, and 58 who tested the old interface. 38 participants were in E1, 38 participants were in E2, and 40 participants were in E3. Since our experiment ended after 40 minutes, we chose to assign the max time of 40:08 minutes to participants who did not succeed. Table~\ref{table:participant-summary} summarizes the rate of success and time to success for our participants' based on their interface version and environment combination.

@@

Table~\ref{tab:attempts-bridge-proxy} shows the configuration settings of the first successful bootstrap in each environment and interface combination. Note that only four of the default bridges were used to connect successfully for the first time. Users avoid making decisions when a recommendation is given and tend to avoid/fail with more advanced options. Participants who were in environments in that the recommended bridge (obfs3) worked did not configure another bridge, not taking advantage of the various default bridges available to them. Participants who were in environment that required a meek or custom bridge only were able to succeed with a meek bridge.

@@

In our experiment, participants had 40 minutes to circumvent censorship. Fig.~\ref{fig:time_to_success_ecdf} shows the cumulative success rates over time. Participants were less and less likely to succeed as time went on. Users in the wild will likely not be motivated to configure their connection for 40 minutes. If users were only willing to put in a minute or so of their time, users in intermediate and heavily censored environments will be unable to connect. Even if users were willing to dedicate 10 minutes to configuring their connection, most users in heavily censored environments will be unable to connect. Ideally, users should be able to connect to Tor within a couple of minutes, regardless of their censorship environment. We propose ideas on how to achieve this in section~\ref{recommendations}.

\begin{figure}
\centering
\includegraphics{time_to_success_ecdf}
	% Generated by info.R:
	\begin{tabular}{l r r r r}
	& \multicolumn{1}{c}{1.5~m} & \multicolumn{1}{c}{10~m} & \multicolumn{1}{c}{20~m} & \multicolumn{1}{c}{40~m} \\
	\noalign{\hrule}
	E1-NEW & 100\% & 100\% & 100\% & 100\% \\
	E1-OLD & 58\% & 100\% & 100\% & 100\% \\
	E2-NEW & 11\% & 79\% & 89\% & 95\% \\
	E2-OLD & 16\% & 68\% & 79\% & 84\% \\
	E3-NEW & 0\% & 25\% & 45\% & 65\% \\
	E3-OLD & 0\% & 20\% & 25\% & 50\% \\
	\end{tabular}
\caption{
Cumulative success rates over time, by censorship environment and interface.
We stopped participants after 40 minutes. Here, those who did not finish were assigned
an arbitrarily high number greater than 40 minutes for the purposes of plotting. 
For example, every E1-NEW participant finished within 90 seconds,
but only 58\% of E1-OLD had finished by that time.
After 10 minutes, 79\% of E2-NEW and 68\% of E2-OLD had finished.
After 20 minutes, 45\% of E3-NEW and only 25\% of E3-OLD had finished.
}
\label{fig:time_to_success_ecdf}
\end{figure}

@@

\begin{figure*}
\centering
\includegraphics{all-participant-edges}
\caption{
Summary of participants' actions throughout the entire experiment.
Different colors indicate which screen was shown at each moment.
The narrow black lines show the times when the configuration interface
was not running; i.e., a participant was doing something else
such as searching the web in another browser.
The overall length of the lines show the total time to completion,
except for those we cut off after approximately 40 minutes.
}
\label{fig:all-participant-edges}
\end{figure*}

@@

Perhaps a more meaningful measurement of time is the amount of times participants actively spent configuring their connection. We define this as the amount of time that participants spent on the interface, except for time spent on the progress screen. This is a simplified notion active configuration time, since some participants searched for help on the web while they were waiting. However, this behavior was equally likely in the new and old interface conditions.

@@

\begin{description}
%connect vs configure
\item {\bfseries Users try the easy path first.} Users still do not seem to know how to differentiate between censored websites and censored tor relays, and just try the easy option to connect directly to the Tor network first, leaking that they are connecting to Tor on the network.  81\% (94 of 116) of first attempts were to connect directly, 86\% (50 of 116) from the new interface and 76\% (44 of 116) from the old interface.

% impacts of making the proxy page ``automated'' 
\item {\bfseries Users wasted time configuring proxies.} Users believe that they needed proxies to connect. This confusion prevented users from configuring their bridges correctly. Participants with the new interface who were explicitly told that they did not need a proxy spent 31\% of their active time configuring proxies and participants in the old interface who did not receive feedback spent 63\%.

@@

\subsubsection{Reasons for Failure} 
Failure is common. 64\% (74 of 116) of first attempts to connect failed and 79\% (376 of 462) of total attempts to connect failed. 20\% (21 of 116) of participants failed entirely. Reasons for failure were determined by a combination of log processing (i.e. how much time was spent on a particular screen) and video observation (i.e. observing what they searched for online). \\

\begin{description}
\item {\bfseries Only connected directly. (7/21)} These participants tried a direct connection. When that failed, they tried the same configuration, over and over, without trying other configurations, no matter how many times they failed. It was common to restart the interface, check Internet settings, and wait between subsequent attempts. 
\item {\bfseries Didn't know what to do next. (6/21)} After a failed direct connection and a failed default obfs3 bridge connection, these participants did not know what to do next. They often tried those configurations again or gave up. 
\item {\bfseries Thought that they needed a proxy (5/21)} After a couple failed attempts, these participants assumed that they needed a proxy. They spent the time trying to configure a proxy, usually without trying other bridges. 
\item {\bfseries Used the bridges auto-responder incorrectly (2/21)} Three participants in our heavy censorship environment figured that the recommended bridge and most hard-coded bridges were not working and found the auto-responder through the help button. However, they all failed to get a response. For details, see Appendix~\ref{failed-participants}.
\end{description}

We discarded data on participants who chose to download their own version of Tor Browser online. Some downloaded their own version without trying the provided one on their desktop, while others did so after feeling frustrated with the provided version. Appendix~\ref{tor-downloads} gives the unfortunate details the of where Tor was downlaoded when torproject.org was blocked.

@@

We did not test cases in which the user is required to configure a custom bridge or proxy. Our participants were from one geographic location in the United States and are able to speak English.

\section{Future Work} 
Throughout the qualitative user study, redesign of the interface, and the quantitative user study, we collaborated and communicated with Tor developers. Redesigning the configuration interface was a mutual interest. In fact, Tor version {\color{red} 5.?.?} incorporated textual and navigational changes based on our redesigned interface. We plan to work with Tor developers to integrate helpful changes. This process will entail debugging our code, merging changes with the current version of Tor, making high-fidelity graphics that align with style guides, and finalizing the advice to give to users in the interface.

@@

\begin{description}
\item{\bfseries Automate the configuration.} Complete automation and network probing sounds like a radical idea, but this wouldn't harm users today (as far as we know). Most users would leak that they are using Tor when trying to circumvent an advanced censor, since most first attempts to connect fail. 
\item{\bfseries Ask about the risk.} Ask the users if they would be at risk if the process was automated, and automate the configuration process for all who are not at risk. The ones at risk will configure manually. The complication with this approach is that users may not be qualified to answer this question or may not trust Tor to answer honestly. 
\item{\bfseries Ask if users if they know what to do.} We ask users if they know how to configure a bridge and proxy, and automate the configuration process if they do not. However, there are ethical implications of making mistakes on behalf of the users if there is risk involved. 
\end{description}

@@

\section {Acknowledgments}
I want to especially thank Rowilma del Castillo of Xlab for supporting the experiment, assisting with testing, and being flexible with non-Xlab recruting. I have received much valuable feedback from Nima Fatemi, Isabela Bagueros, Georg Koppen, and the Tor UX team.

\section {Resources} 
For additional details, such as the censorship simulation code, interview transcriptions, and logs of participant interactions, we refer you to the project repository: \\

\noindent https://github.com/lindanlee/circumvention-ux-tor

\section{Conclusion} 
We conducted a series of experiments to improve the Tor 5.0.3 Tor launcher configuration interface, which helps users circumvent censorship using Tor. The qualitative user study interviews 16 pre-screened participants about their experience trying to circumvent mild, intermediate, and heavy censorship with the current interface, giving insight into common challenges in configuring a connection, such as confusing the necessity of bridges and proxies, assuming that a correct configuration was wrong due to a progress bar bug, and not knowing what to do on failure. This feedback is used to guide the redesign of the configuration interface.

We test the impact of our changes on 116 participants in the quantitative user study to find that that the changes made cause a statistically significant reduction in the time participants spent configuring their connection, with no decrease in success rates. We observe and quantify common behavioral trends based on logs and video recordings of our participants, and offer recommendations that we believe will greatly increase the success rate and time to success for future users.

@@

Only tried to connect directly (7/21): 
\begin{itemize}
\item E2-NEW-X21-20160323-1400
\item E2-OLD-X04-20160330-1800
\item E2-OLD-X10-20160331-1600
\item E3-NEW-X05-20160324-1400
\item E3-NEW-X17-20160323-1400
\item E3-OLD-X06-20160330-1600
\item E3-OLD-X12-20160330-1800
\end{itemize}

Didn't know what to do next (6/21): 
\begin{itemize}
\item E3-NEW-X11-20160330-1600
\item E3-NEW-X11-20160331-1800
\item E3-NEW-X23-20160323-1400
\item E3-OLD-X06-20160331-1800
\item E3-OLD-X12-20160331-1600
\item E3-OLD-X30-20160328-1400
\end{itemize}

Thought that they needed a proxy (5/21): 
\begin{itemize}
\item E2-OLD-X10-20160328-1400
\item E3-NEW-X17-20160328-1600
\item E3-OLD-X06-20160325-1800
\item E3-OLD-X06-20160330-1800
\item E3-OLD-X24-20160328-1600
\end{itemize}
